\vspace{-1em}\thetitle

### 2009-08-14 paper.tex
...

\begin{table*}
\begin{center}
\small
\begin{tabular}{|c|c|c|c|c|c|c|}

\hline
\textbf{Trace} &
\textbf{Year} &
\textbf{Start} &
\textbf{End} &
\textbf{Type} &
\textbf{Network} \\
\hline

{\footnotesize{DARTMOUTH}} &
2003 &
Mon Nov  3 18:39:48 &
Wed Nov  5 16:09:48 &
campus &
Dartmouth College campus \\
\hline

{\footnotesize{IETF 60}} &
2004 &
Wed Aug  4 17:02:50 &
Wed Aug  4 18:02:49 &
conference &
IETF hotel venue \\
\hline

{\footnotesize{IETF 67}} &
2006 &
Wed Nov  8 19:31:56 &
Wed Nov  8 20:18:29 &
conference &
IETF hotel venue \\
\hline

{\footnotesize{SIGCOMM 2001}} &
2001 &
Wed Aug 29 17:24:47 &
Fri Aug 31 19:53:15 &
conference &
SIGCOMM hotel venue \\
\hline

{\footnotesize{SIGCOMM 2004}} &
2004 &
Tue Aug 31 13:25:04 &
Fri Sep  3 21:40:22 &
conference &
SIGCOMM hotel venue \\
\hline

{\footnotesize{UCSD}} &
2007 &
Thu Jan 11 07:59:50 &
Fri Jan 12 07:59:55 &
campus &
UCSD engineering building \\
\hline

\end{tabular}
\caption{Traffic traces used for analysis and experiments.}
\tab{traces}
\end{center}
\vspace{-2.5em}
\end{table*}

>>>>

\begin{table}
\begin{center}
\small
\begin{tabular}{|c|c|c|c|c|c|c|}

\hline
\textbf{Trace} &
\textbf{Year} &
\textbf{Type} &
\textbf{Network} \\
\hline

{\scriptsize{DARTMOUTH}} &
2003 &
campus &
Dartmouth College \\
\hline

{\scriptsize{IETF 60}} &
2004 &
conference &
IETF hotel \\
\hline

{\scriptsize{IETF 67}} &
2006 &
conference &
IETF hotel \\
\hline

{\scriptsize{SIGCOMM 2001}} &
2001 &
conference &
SIGCOMM hotel \\
\hline

{\scriptsize{SIGCOMM 2004}} &
2004 &
conference &
SIGCOMM hotel \\
\hline

{\scriptsize{UCSD}} &
2007 &
campus &
UCSD engineering \\
\hline

\end{tabular}
\caption{Traffic traces used for analysis and experiments.}
\tab{traces}
\end{center}
\vspace{-2.5em}
\end{table}
